Validation of Visual Statistical Inference, Applied to Linear Models

### 2012-05-29 paper_jasa.tex
power with effect for experiment 1and 2

\begin{figure*}[hbtp]
   \centering
       \scalebox{0.7}{\includegraphics{effect_power_exp1.pdf}}
       \caption{Observed power shown by loess smoother and the power of UMP test for different effect size $E$ as per experiment 1.}
       \label{fig:power_effect1}
\end{figure*}

\begin{figure*}[hbtp]
   \centering
       \scalebox{0.7}{\includegraphics{effect_power_subject_exp1.pdf}}
       \caption{Subject specific power obtained from equation \ref{eqn:effect} and the power of UMP test for different effect size $E$ as per experiment 1.}
       \label{fig:power_effect_subject1}
\end{figure*}

>>>>

\begin{figure*}[hbtp]
   \centering
       \scalebox{0.45}{\includegraphics{effect_power_exp1.pdf}}
       \scalebox{0.45}{\includegraphics{effect_power_exp2.pdf}}
       \caption{Observed power shown by loess smoother and the power of UMP test for different effect size $E$ as per experiment 1 and 2.}
       \label{fig:power_effect1}
\end{figure*}

\begin{figure*}[hbtp]
   \centering
       \scalebox{0.45}{\includegraphics{effect_power_subject_exp1.pdf}}
       \scalebox{0.45}{\includegraphics{effect_power_subject_exp2.pdf}}
       \caption{Subject specific power obtained from equation \ref{eqn:effect} and the power of UMP test for different effect size $E$ as per experiment 1 and 2.}
       \label{fig:power_effect_subject1}
\end{figure*}
